Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-07-14 main.tex
swap item in list.
In the text swarm algorithm is explained first and then
evolutionary. I think the list should follow the same
order, the reading flow is better.
corrections
Typos and fix labels for chapters 4 and 5.

\subsection{ANN: Single Hidden Layer Artificial Neural Network}

@@

\subsection{Hidden Markov Models}

@@

\begin{itemize}
    \item Evolutionary algorithm: \cite{moriarty1999evolutionary}.
    \item Particle Swarm Algorithm: \cite{imran2013overview}.
\end{itemize}

@@

\begin{itemize}
 \item total or mean payoff
 \item total or mean payoff difference (unused in this work)
 \item total Moran process wins (fixation probability). This lead to the
     strategies named TF1, TF2, TF3 listed in
     Appendix~\ref{app:list_of_players}.
\end{itemize}

These can be used in Noisy or Standard environments (as evidenced by
Sections~\ref{sec:standard} and~\ref{sec:noisy}). These objectives can be
further modified to suit other purposes. New strategies could be trained with
variations including spatial structure and probabilistically ending matches.

>>>>

\subsection{ANN: Single Hidden Layer Artificial Neural Network}\label{sec:ann}

@@

\subsection{Hidden Markov Models}\label{sec:hmm}

@@

\begin{itemize}
    \item Particle Swarm Algorithm: \cite{imran2013overview}.
    \item Evolutionary algorithm: \cite{moriarty1999evolutionary}.
\end{itemize}

@@

\begin{itemize}
 \item total or mean payoff,
 \item total or mean payoff difference (unused in this work),
 \item total Moran process wins (fixation probability). This lead to the
     strategies named TF1, TF2, TF3 listed in
     Appendix~\ref{app:list_of_players}.
\end{itemize}

These can be used in noisy or standard environments (as evidenced by
Sections~\ref{sec:standard} and~\ref{sec:noise}). These objectives can be
further modified to suit other purposes. New strategies could be trained with
variations including spatial structure and probabilistically ending matches.
